% User's resume LaTeX
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article} % Set font size to 12pt

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage[utf8]{inputenc}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

% \newcommand{\classesList}[4]{
%     \item\small{
%         {#1 #2 #3 #4 \vspace{-2pt}}
%   }
% }

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

% \newcommand{\resumeSubSubheading}[2]{
%     \item
%     \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
%       \textit{\small#1} & \textit{\small #2} \\
%     \end{tabular*}\vspace{-7pt}
% }

% \newcommand{\resumeProjectHeading}[2]{
%     \item
%     \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
%       \small#1 & \textbf{\small #2}\\
%     \end{tabular*}\vspace{-7pt}
% }

% \newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*, itemsep=1pt, topsep=0pt, parsep=0pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
  {\scshape \LARGE Satyajeet Kudalkar} \\[4pt]
  {\small Pune, India \textbullet{} Open to relocation \textbullet{} Targeting Canada} \\[6pt]
  {\small
    \href{tel:+918055823724}{+91 80558-23724} \quad | \quad
    \href{mailto:kudalkarsatyajeet@gmail.com}{kudalkarsatyajeet@gmail.com} \quad | \quad
    \href{https://www.linkedin.com/in/satyakudalkar/}{linkedin.com/in/satyakudalkar}
  }
\end{center}


\vspace{-14pt}
%-----------Professional Summary-----------
\section{Professional Summary}

\small{
    \begingroup \setlength{\parskip}{2pt}
    Senior Software Engineer with 6+ years of experience designing and delivering cloud-native backend systems and cross-platform SDKs. Expert in Java and Spring Boot, and deeply experienced in \textbf{Kotlin Multiplatform (Android, iOS, Web JS)} for building and maintaining SDKs used by downstream customers. Strong background in microservices, event-driven architectures, PCI-DSS requirements, and CI/CD (GitHub Actions, Jenkins, Changesets). Proven track record of troubleshooting client integrations, Experienced in Java 8+, Spring ecosystem, SQL optimization, multithreading, and performance tuning. Actively pursuing relocation to Canada under the Global Talent Stream and open to immediate international opportunities.
    \endgroup
}
\vspace{-2pt}




%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
  {AISSMS Institute of Information Technology}{2016 -- 2019}
  {Bachelor of Engineering in Information Technology}{Pune, Maharashtra, India}

\resumeSubheading
  {PVPIT Budhgaon}{2013 -- 2016}
  {Diploma in Computer Engineering}{Sangli, Maharashtra, India}

\resumeSubHeadingListEnd
\vspace{-10pt}
%-----------Technical Skills-----------
\section{Technical Skills}
% \begin{itemize}[leftmargin=0.15in, label={}]
\begin{itemize}[leftmargin=0.15in, label={}, itemsep=0pt, parsep=0pt, topsep=0pt]
\small{\item{\textbf{Languages \& Frameworks:} Java, Kotlin, Spring Boot, Kotlin Multiplatform (KMP - Android/iOS/Web JS), REST APIs, Microservices, JUnit, Cucumber, Mockito}}
\small{\item{\textbf{Cloud \& Infrastructure:} Google Cloud Platform (GCP), App Engine, Docker, Kubernetes (exposure), CI/CD: GitHub Actions, Jenkins, Changesets}}
\small{\item{\textbf{Databases \& Messaging:} PostgreSQL, MySQL, Cassandra, BigQuery, Couchbase, Google Pub/Sub, NATS}}
\small{\item{\textbf{Tools \& Practices:} Git, Maven, Gradle, Bitbucket, Rally, Agile, Automated testing, Semantic versioning, Release management}}
\small{\item{\textbf{Security \& Compliance:} PCI DSS awareness, cryptographic APIs, secure key management}}
\end{itemize}


%-----------Certifications-----------
% Define a custom list for certifications with a reduced item separation
% \newlist{certifications}{itemize}{1}
% \setlist[certifications]{label=\textbullet, topsep=0pt, itemsep=-2pt, leftmargin=*}

% % Use the custom certifications list for your certifications section
% \section{Certifications}
% \begin{certifications}
% \item {\textbf{Core Java and Android app development.}}  \hfill 
%  \item {\textbf{React: The Complete Guide.}} \hfill 
% \end{certifications}

\vspace{-4pt}
%-----------EXPERIENCE-----------
\section{Work Experience}
\resumeSubHeadingListStart

\resumeSubheading
  {Senior Software Engineer}{Jan 2025 -- Present}
  {Vonage}{Remote / Pune, India}
  \vspace{0pt}
  \resumeItemListStart
    \resumeItem{Led development and maintenance of the core \textbf{Kotlin Multiplatform (KMP) SDK} across \textbf{Android, iOS, and Web JS}, ensuring feature parity and platform stability.}
    \resumeItem{Implemented and executed comprehensive testing strategies (manual + automated) across platforms to catch platform-specific regressions prior to releases.}
    \resumeItem{Owned the end-to-end SDK release process: semantic versioning, changelog management, automated validations, and publishing to platform registries.}
    \resumeItem{Enhanced CI/CD validations using \textbf{GitHub Actions} and Changesets to enforce release hygiene and avoid breakages.}
    \resumeItem{Collaborated directly with customer engineering teams to triage and resolve SDK integration issues, debug platform-specific bugs, and deliver timely fixes.}
    \resumeItem{Conducted cross-team \textbf{code reviews} and provided technical guidance to improve code quality, observability, and stability.}
  \resumeItemListEnd
  
\vspace{8pt}

\resumeSubheading
  {Software Engineer II}{Jan 2022 -- Nov 2024}
  {Mastercard}{Pune, India}
    \vspace{0pt}
  \resumeItemListStart
    \resumeItem{Designed and developed \textbf{PCI-DSS compliant microservices} using \textbf{Spring Boot}, \textbf{NATS}, and \textbf{Axon}, enabling secure, event-driven payment processing across global markets.}
    \resumeItem{Contributed to a major network switch launch in South Africa with \textbf{100\% Day-1 success}, supporting multiple customers and ensuring seamless deployment through robust CI/CD pipelines.}
    \resumeItem{Built a reliable \textbf{store-and-forward} messaging system with scheduled retries using \textbf{PostgreSQL}, reducing downstream delivery failures.}
    \resumeItem{Developed a \textbf{stream-to-batch} transformation service converting real-time Axon/NATS events into ISO-compliant batch files (T112, T113) for Mastercard settlements.}
    \resumeItem{Integrated and extended \textbf{cryptographic APIs} for secure key management and card data protection, improving security.}
  \resumeItemListEnd

\vspace{8pt}

\resumeSubheading
  {Software Developer}{Jul 2019 -- Jan 2022}
  {Bitwise}{Pune, India}
    \vspace{0pt}
  \resumeItemListStart
    \resumeItem{Developed microservices on \textbf{GCP App Engine} to deliver real-time chargeback and settlement notifications for a unified commerce platform supporting \textbf{Google as a merchant}.}
    \resumeItem{Built scalable data-processing components using \textbf{Google Pub/Sub} and \textbf{Spring Boot}, enabling reliable event ingestion and downstream communication.}
    \resumeItem{Led development of the internal EI Web App using \textbf{Java}, \textbf{Spring Boot}, \textbf{CloudSQL}, and \textbf{GMail API}, improving team communication and operational visibility across engineering groups.}
  \resumeItemListEnd

\resumeSubHeadingListEnd
\end{document}
